### 2013-04-17 doc/final_report/design.tex
Added some punctuation corrections

Despite the use of an iterative development methodology, some of the key
components within Partridge were designed 'up front' in order to accelerate
implementation and reduce the time needed to add new components to the
system. The components that make up Partridge and the ways in which they react
are described and analysed below; choices regarding the type of application,
the target audience and the programming environment are also discussed.

@@

The final stage in the preprocessor pipeline is paper classification. During
this stage, features will be extracted from the papers and used to classify the
paper in three different ways. The paper's type: case study or review paper
etc. will be determined using the presence or absence of different CoreSC labels
within the paper and their relative proportions. The subject of paper will be
determined by the presence of domain specific nouns and adjectives within the
paper. For example, a biology paper might contain words such as 'enzyme' or 'amino
acid.' The result of the paper, i.e. whether the paper was conclusive and if the
results were positive or negative, will be detected through the presence or absence
of words with a strong sentiment polarity as discussed by Wilson et al
(2005)\cite{Wilson05Polarity}. The results from the whole process are then
passed into the data store and saved.

>>>>

Despite the use of an iterative development methodology, some of the key
components within Partridge were designed `up front' in order to accelerate
implementation and reduce the time needed to add new components to the
system. The components that make up Partridge and the ways in which they react
are described and analysed below; choices regarding the type of application,
the target audience and the programming environment are also discussed.

@@

The final stage in the preprocessor pipeline is paper classification. During
this stage, features will be extracted from the papers and used to classify the
paper in three different ways. The paper's type: case study or review paper
etc. will be determined using the presence or absence of different CoreSC labels
within the paper and their relative proportions. The subject of paper will be
determined by the presence of domain specific nouns and adjectives within the
paper. For example, a biology paper might contain words such as `enzyme' or `amino
acid.' The result of the paper, i.e. whether the paper was conclusive and if the
results were positive or negative, will be detected through the presence or absence
of words with a strong sentiment polarity as discussed by Wilson et al
(2005)\cite{Wilson05Polarity}. The results from the whole process are then
passed into the data store and saved.

### 2013-04-17 doc/final_report/report.tex
Added some punctuation corrections

I would like to take this opportunity to thank both of my
supervisors, Amanda Clare and Maria Liakata, for giving up so much of their
time to support me in designing and developing this project.

>>>>

I would like to take this opportunity to thank both of my
supervisors, Dr Amanda Clare and Dr Maria Liakata, for giving up so much of their
time to support me in designing and developing this project.
